State of the Practice for Medical Imaging Software

### 2021-12-07 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP_AcademicRadiology.tex
Changed use of italics to be more consistent, fixed spelling mistake

The repository measures help us in wo ways. Firstly, they help us with get a
fast and accurate project overview. For example, the number of commits over the
last 12 months shows how active a project has been, and the number of stars and
forks may reveal its popularity. Secondly, the results may affect our decisions
regarding the grading scores for some software qualities. For example, if the
percentage of comment lines is low, we double-check the
\textit{understandability} of the code; if the ratio of open versus closed pull
requests is high, we pay more attention to \textit{maintainability}.

@@

Figure \ref{fg_visibility_transparency_scores} shows the AHP scores for
\textit{visibility/transparency}. Generally speaking, the teams that actively
documented their development process and plans scored higher. Table
\ref{tab_Visibility/Transparency_docs} shows the projects that had documents for
the development process, project status, development environment, and release
notes, in the descending order of their visibility/transparency scores.
%This table contains part of the answers to \hyperlink{rq1}{RQ1} and \hyperlink{rq3}{RQ3}.

@@

Project \textit{dwv} was popular on GitHub, but we ranked it low. As mentioned
in Section~\ref{sec_result_installability}, we failed to build it locally, and
used the test version on its websites for the measurements. We followed the
instructions and tried to run the command ``yarn run test'' locally, which did
not work. In addition, the test version did not detect a broken DICOM file and
displayed a blank image as described in Section \ref{sec_result_robustness}. We
might underestimate the scores for \textit{dwv} due to uncommon technical
issues. We also ranked \textit{DICOM Viewer} much lower than its popularity. As
mentioned in Section \ref{sec_result_installability} it depended on the
NextCloud platform that we could not successfully install. Thus, we might
underestimate the scores of its \textit{surface reliability} and \textit{surface
robustness}. We weighted all qualities equally, which is not likely to be the
case with all users. As a result, some projects with high popularity may not
perform well in all qualities.

@@

As shown in Section~\ref{sec_software_selection}, our domain experts recommended
a list of top software with 12 software products.  All of the top 4 software
from the Domain Expert's list are among the top 12 ranked by our methodology. 3
of the top 4 on both lists are the same: \textit{3D Slicer}, \textit{ImageJ},
and \textit{Fiji}. \textit{3D Slicer} is top project by both rankings (and by
the GithHub stars measure as well).  The Domain Expert ranked \textit{Horos} as
their second choice, while we ranked it twelth.  Our third ranked project,
\textit{OHIF Viewer} was not listed by the Domain Expert.  Neither were the
software packages that we ranked from fifth to eleventh (\textit{ParaView},
\textit{Weasis}, \textit{medInria}, \textit{BioImage Suite Web}, \textit{OsiriX
Lite}, \textit{INVESALIUS}, and \textit{Gwyddion}).  The software mentioned by
the Domain Expert that we did not rank were the six recommended packages that
did not have visualization as the primary function (as discussed in
Section~\ref{sec_software_selection}).  The differences between the list
recommended by our methodology and the Domain Expert are not surprising.  As
mentioned above, the methodology weights all qualities equally, but that may not
be the case for the Domain Expert's impressions.  Moreover, although the Domain
Expert has significant experience with MI software, he has not used every one of
the 29 packages.

@@

>>>>

The repository measures help us in wo ways. Firstly, they help us with get a
fast and accurate project overview. For example, the number of commits over the
last 12 months shows how active a project has been, and the number of stars and
forks may reveal its popularity. Secondly, the results may affect our decisions
regarding the grading scores for some software qualities. For example, if the
percentage of comment lines is low, we double-check the
understandability of the code; if the ratio of open versus closed pull
requests is high, we pay more attention to maintainability.

@@

Figure \ref{fg_visibility_transparency_scores} shows the AHP scores for
visibility/transparency. Generally speaking, the teams that actively
documented their development process and plans scored higher. Table
\ref{tab_Visibility/Transparency_docs} shows the projects that had documents for
the development process, project status, development environment, and release
notes, in the descending order of their visibility/transparency scores.
%This table contains part of the answers to \hyperlink{rq1}{RQ1} and \hyperlink{rq3}{RQ3}.

@@

Project \textit{dwv} was popular on GitHub, but we ranked it low. As mentioned
in Section~\ref{sec_result_installability}, we failed to build it locally, and
used the test version on its websites for the measurements. We followed the
instructions and tried to run the command ``yarn run test'' locally, which did
not work. In addition, the test version did not detect a broken DICOM file and
displayed a blank image as described in Section \ref{sec_result_robustness}. We
might underestimate the scores for \textit{dwv} due to uncommon technical
issues. We also ranked \textit{DICOM Viewer} much lower than its popularity. As
mentioned in Section \ref{sec_result_installability} it depended on the
NextCloud platform that we could not successfully install. Thus, we might
underestimate the scores of its surface reliability and surface
robustness. We weighted all qualities equally, which is not likely to be the
case with all users. As a result, some projects with high popularity may not
perform well in all qualities.

@@

As shown in Section~\ref{sec_software_selection}, our domain experts recommended
a list of top software with 12 software products.  All of the top 4 software
from the Domain Expert's list are among the top 12 ranked by our methodology. 3
of the top 4 on both lists are the same: \textit{3D Slicer}, \textit{ImageJ},
and \textit{Fiji}. \textit{3D Slicer} is top project by both rankings (and by
the GithHub stars measure as well).  The Domain Expert ranked \textit{Horos} as
their second choice, while we ranked it twelfth.  Our third ranked project,
\textit{OHIF Viewer} was not listed by the Domain Expert.  Neither were the
software packages that we ranked from fifth to eleventh (\textit{ParaView},
\textit{Weasis}, \textit{medInria}, \textit{BioImage Suite Web}, \textit{OsiriX
Lite}, \textit{INVESALIUS}, and \textit{Gwyddion}).  The software mentioned by
the Domain Expert that we did not rank were the six recommended packages that
did not have visualization as the primary function (as discussed in
Section~\ref{sec_software_selection}).  The differences between the list
recommended by our methodology and the Domain Expert are not surprising.  As
mentioned above, the methodology weights all qualities equally, but that may not
be the case for the Domain Expert's impressions.  Moreover, although the Domain
Expert has significant experience with MI software, he has not used every one of
the 29 packages.

@@

TO DO

- add more on comparison to existing literature surveys
- ask Mike:
    - for journal version ask for more figures?
